Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-26 Arxiv/main.tex
rewrite sliding property

\section{Mechanism Proposition}
\label{sec_mechs}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
\[
  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
\]
where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
Notice that $\candidateset$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

@@

\subsubsection{Exponential Mechanism}
Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
\begin{equation*}
\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\end{equation*}
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\end{equation*}

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\sum_{r'\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\Big)}.
\end{equation*}
where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

@@

This mechanism is based on the basic exponential mechanism
\cite{talwar}, with $\candidateset$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$.

@@

This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-multinomial system.

@@

\noindent \textbf{Sliding Property of $\hexpmech$}
\begin{lem}
\label{lem_sliding}
Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta')$, $\epsilon\geq 0$ and $|\delta'| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
\end{equation*}

\end{lem}

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ of every
 $r\in\candidateset$ and the probability 
 $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) =
 \hellinger(\bysinfer(\dataobs),r)]$ for the utility score of $r \in \candidateset$.

 Let $|z|$ be the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e. $u(z,\dataobs) = u(r,\dataobs)$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.

 % It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
 % let $R_1, R_2 \subset \candidateset$ be a partition of $\candidateset$, where every $z \in R_1$ has a distinct score, i.e., $|z| = 1$ and $z \in R_2$ has another $z' \in R_2$ with the same score, i.e., $|z| = 2$. The proofs are given by parts:

		We denote the normalizer of the probability mass in $\hexpmech(\dataobs)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(\dataobs)})$ as $NL(\dataobs)$:
		\begin{equation*}
		\begin{split}
		LHS 
		  = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
		& = |z| \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
		\end{split}
		\end{equation*}

		By bounding the $\delta' \geq -S(\dataobs)$, we can get:

		\begin{equation*}
		\begin{split}
		|z|  \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
		&  \leq |z| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = (\delta' + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}

@@

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = e^{\lambda} c] + \frac{\delta'}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.

@@

\textbf{Detail proof:}
	To show:
	\begin{equation*}
	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)]
	\leq
	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} u(r,\dataobs)] + \frac{\delta'}{2},
	\end{equation*}
  we need to show:
  \begin{equation*}
  Pr[u(\hexpmech(\dataobs), \dataobs) = u(r,\dataobs)]
  \leq
  e^{\frac{\epsilon}{2}} Pr[u(\hexpmech(\dataobs), \dataobs) = e^{\lambda} u(r,\dataobs)] + \frac{\delta'}{2},
  \end{equation*}

@@

		Based on the accuracy property of exponential mechanism:
		\begin{equation*}
		\begin{split}
		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
		\end{split}
		\end{equation*}
		we derived the accuracy bound for $\hexpmech$:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] 
		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
		\end{split}
		\end{equation*}

@@

		Particularly in Beta-binomial system, $|\candidateset| = n + 1$, then it is enough to set $\gamma$ as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |n + 1|})})$.

@@

For all $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$, we need to show that:
\begin{equation*}
\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[z = r] + \delta. 
\end{equation*}

	Given that $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(r, \dataobs)$, $U_1 = u(z, \dataobs') - u(z, \dataobs$), $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$. Then,

	Given that $2\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big) = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(z, \dataobs) = u(r, \dataobs)]$, let $U = u(\dataobs,r)$, $U_1 = u(z, \dataobs') - u(z, \dataobs)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$. Then,

>>>>

\section{Mechanism Proposition}
\label{sec_mechs}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
\[
  \candidateset{\dataobs}\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
\]
where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
Notice that $\candidateset{\dataobs}$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset{\dataobs}$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

@@

\subsubsection{Exponential Mechanism}
Exponential mechanism $\expmech{}{x}{u}{\candidateset{\dataobs}}$ samples a element from the candidate set $\candidateset{\dataobs} = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
\begin{equation*}
\underset{z \thicksim \expmech{}{x}{u}{\candidateset{\dataobs}} }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\end{equation*}
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset{\dataobs}}$ share the same candidate set and utility function as it with standard exponential mechanism. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset{\dataobs}}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\end{equation*}

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset{\dataobs}$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\nomalizer{\dataobs}}.
\end{equation*}
where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

@@

This mechanism is based on the basic exponential mechanism
\cite{talwar}, with $\candidateset{\dataobs}$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$.

@@

This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset{\dataobs}$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset{\dataobs}$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-multinomial system.

@@

In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$, we first introduce Lemma \ref{lem_score_pro_convert} and \ref{lem_cadinality}.

\begin{lem}
\label{lem_score_pro_convert}
  Given $\hexpmech(\dataobs)$ and $r', r'' \in \candidateset{\dataobs}$, then following holds:
  $$
  \ux{r'} = \ux{r''} \iff \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
  $$  
\end{lem}
\begin{proof} of lemma \ref{lem_score_pro_convert}.
\begin{itemize}
  \item $\implies$
  \begin{equation*}
  \begin{split}
  \ux{r'} = \ux{r''} 
  & \implies \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
  & \implies Pr[\hexpmech(\dataobs) = r'] = Pr[\hexpmech(\dataobs) = r''] \\
  & \implies \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
  \end{split}
  \end{equation*}

  \item $\impliedby$

    \begin{equation*}
  \begin{split}
  & \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''} \\
  & \implies Pr[\hexpmech(\dataobs) = r'] = Pr[\hexpmech(\dataobs) = r'']\\
  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
  & \implies  \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
  & \implies \ux{r'} = \ux{r''}.
  \end{split}
  \end{equation*}
\end{itemize}

@@

\begin{definition}
\label{def_cardinality}
  $\cardinality{r}$

  Define $\cardinality{r}$ as the cardinality of $R_r$ s.t. $ R_r = \{ r' : \ux{r'} = \ux{r}, r' \in \candidateset{\dataobs}\} \subset \candidateset{\dataobs}$ and $\forall \hat{r} \in \candidateset{\dataobs}, \hat{r} \notin R_r \implies \ux{\hat{r}} \neq \ux{r}$, 
\end{definition}

\begin{lem}
\label{lem_cadinality}
 Given $\hexpmech(\dataobs)$, then the following property holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}
 \end{equation*}
\end{lem}
\begin{proof} of Lemma \ref{lem_cadinality}.\\
To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
$\iff $ to compute $\hexpmechPr{\dataobs}{ R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
By Definition \ref{def_cardinality}, $R_r$ is this set.\\
$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{R_r} $.\\
By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
Apply Lemma \ref{lem_score_pro_convert} in $R_r$, \\
$\implies$ for any $r', r''\in R_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
$\implies$ $\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
\end{proof}

\noindent \textbf{Sliding Property of $\hexpmech$}

\begin{lem}
\label{lem_sliding}

Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. In Beta-binomial system, let $\epsilon\geq 0$ and $\ux{r} + k >=0$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
\end{equation*}
\end{lem}

\begin{proof} of Lemma \ref{lem_sliding}:

Let $\ux{t} = \ux{r} + k$.
In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$:
\begin{itemize}
  \item[-] $\cardinality{r} = 1$, $\ux{r} = 0$,  containing only the correct posterior.
  \item[-] $\cardinality{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
\end{itemize}

Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
\begin{itemize}
  \item $\ux{r} \neq 0$, $\ux{r} + k \neq 0$ and $k \geq 0$.\\
  By $\ux{r} + k \neq 0$, $\cardinality{t} = 2$.\\
  By Lemma \ref{lem_score_pro_convert}, $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r} \hexpmechPr{\dataobs}{z = r}$.\\
  By $\ux{r} \neq 0 $, $\cardinality{r} = 2$.\\
  $\implies$\\
    \begin{equation*}
    \begin{split}
    LHS 
    & = 2 \cdot \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
    & = RHS.
    \end{split}
    \end{equation*}

  \item $u(\dataobs, r) \neq 0$, $\ux{r} + k \neq 0$ and $-\ux{r} < k < 0$

  \item $\ux{r} = 0$.\\
  By $\ux{r} = 0$, $\cardinality{r} = 1$.\\
  Destruct $k$:
  \begin{itemize}
    \item $k = 0$:\\
    \begin{equation*}
    \begin{split}
    LHS 
    & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + 0}\\
    & = \hexpmechPr{\dataobs}{\ux{z} = \ux{r} + k}\\
    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
    & = RHS.
    \end{split}
    \end{equation*}
    \item $k \neq 0$:\\
    By $\ux{r} + k = k \neq 0$, $\cardinality{t} = 2$.\\
    $\implies$\\
    \begin{equation*}
    \begin{split}
    LHS 
    & = \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
    & < 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
    & = e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
    & \leq e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
    & = RHS.
    \end{split}
    \end{equation*}

  \end{itemize}
  \item $\ux{r} \neq 0, \ux{r} + k = 0$
    By $\ux{r} + k = 0$, $\cardinality{t} = 1$.\\
    By $\ux{r} \neq 0$, $\cardinality{r} = 2$.\\
    $\implies$\\
    \begin{equation*}
    \begin{split}
    LHS 
    & = 2 \cdot \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{- \epsilon k}{2 S(\dataobs)})}{\nomalizer{\dataobs}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = 2 \cdot \frac{exp(\frac{\epsilon (\ux{t})}{2 S(\dataobs)})}{\nomalizer{\dataobs}} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}}\\
    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot 1 \cdot \hexpmechPr{\dataobs}{z = t}\\
    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}\\
    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}} \\
    & = 2 \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
    & = e^{\ln 2} \cdot e^{\frac{- \epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
    & = e^{(\frac{\epsilon k}{S(x)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
    & = RHS.
    \end{split}
    \end{equation*}

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset{\dataobs}|})})$, the dilation property holds:

\begin{equation*}
\hexpmechPr{\dataobs}{u(z,\dataobs) = c}
\leq
e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{u(z,\dataobs) = e^{\lambda} c} + \frac{\delta'}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.

@@

\textbf{Detail proof:}
	To show:
	\begin{equation*}
	\hexpmechPr{\dataobs}{u(z,\dataobs) = u(r,\dataobs)}
	\leq
	e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{u(z,x) = e^{\lambda} u(r,\dataobs)} + \frac{\delta'}{2},
	\end{equation*}
  we need to show:
  \begin{equation*}
  Pr[u(\hexpmech(\dataobs), \dataobs) = u(r,\dataobs)]
  \leq
  e^{\frac{\epsilon}{2}} Pr[u(\hexpmech(\dataobs), \dataobs) = e^{\lambda} u(r,\dataobs)] + \frac{\delta'}{2},
  \end{equation*}

@@

		Based on the accuracy property of exponential mechanism:
		\begin{equation*}
		\begin{split}
		Pr[u(\expmech{}{x}{u}{\candidateset{\dataobs}}) \leq c] 
		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
		\end{split}
		\end{equation*}
		we derived the accuracy bound for $\hexpmech$:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] 
		& \leq |\candidateset{\dataobs}|exp(\frac{\epsilon c}{2 S(\dataobs)}).
		\end{split}
		\end{equation*}

@@

		Particularly in Beta-binomial system, $|\candidateset{\dataobs}| = n + 1$, then it is enough to set $\gamma$ as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |n + 1|})})$.

@@

For all $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$, we need to show that:
\begin{equation*}
\hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[z = r] + \delta. 
\end{equation*}

	Given that $\hexpmechPr{\dataobs}{z = r} = \hexpmechPr{\dataobs}{u(\dataobs,z) = u(\dataobs,r)}$, let $U = u(r, \dataobs)$, $U_1 = u(z, \dataobs') - u(z, \dataobs$), $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$. Then,

	Given that $2\Big( \hexpmechPr{\dataobs}{z = r}\Big) = \hexpmechPr{\dataobs}{u(z, \dataobs) = u(r, \dataobs)}$, let $U = u(\dataobs,r)$, $U_1 = u(z, \dataobs') - u(z, \dataobs)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$. Then,
